\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/badusb.tex

\textbf{Scripting Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
send constructed HID packet to the victim. These constructed HID packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

@@

\textbf{Privacy Extraction Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of USB 3.x; it uses
``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
%text?}. 
The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract sensitive data.

@@

\textbf{Remote Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device remotely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only
the victim's device treat \tool as an external display, but also a valid HID
input source. Hence we can archive complete hijack of victim's device.

>>>>

\textbf{HID Emulation Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
send constructed HID packet to the victim. These constructed HID packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

@@

\textbf{Video Capture Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of USB 3.x; it uses
``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
%text?}. 
The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract sensitive data.

@@

\textbf{Full Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device completely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only
the victim's device treat \tool as an external display, but also a valid HID
input source. Hence we can archive complete hijack of victim's device.
